---
title: "MIS 500 Porfolio"
author: "Michael Pearson"
date: "2/3/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

This is some stuff to get writing going

``` {r data analysis, eval = TRUE}
## Connect to the page and download the zipped files

temp <- tempfile()

download.file("https://archive.ics.uci.edu/ml/machine-learning-databases/00296/dataset_diabetes.zip", temp)

post_zipped <- unzip(temp)

##print(post_zipped)



diabetes_data <- read.csv("./dataset_diabetes/diabetic_data.csv", header = TRUE)

##print(head(diabetes_data))

## Convert to a data table for easier subsetting

## Now convert to a data table so that the genders can be broken out into separate tables for analysis

library(data.table)
library(reshape2)
library(dplyr)
library(ggplot2)
library(vcd)
library(ggpubr)


##print(summary(diabetes_data))
```

Now for some tablature 
## For plotting

## Some stats about the data
```{r bunch of tables, eval =TRUE, include = TRUE}
table(diabetes_data$gender)

table(diabetes_data$race)

table(diabetes_data$weight)

table(diabetes_data$time_in_hospital)

table(diabetes_data$num_lab_procedures)

table(diabetes_data$num_procedures)

table(diabetes_data$readmitted)

table(diabetes_data$diabetesMed)

table(diabetes_data$change)

table(diabetes_data$insulin)


table(diabetes_data$insulin)

table(diabetes_data$examide)

table(diabetes_data$num_medications)

table(diabetes_data$number_outpatient)

table(diabetes_data$number_emergency)

table(diabetes_data$max_glu_serum)

table(diabetes_data$A1Cresult)

table(diabetes_data$number_inpatient)

table(diabetes_data$number_diagnoses)

table(diabetes_data$age)

length(unique(diabetes_data$patient_nbr))
```
This section is where we will check out the full data set

```{r Full Data Set, eval = TRUE}

gender_readmit <- diabetes_data[, c(4,50)]

try <- table(gender_readmit)
gender_readmit_table <- try[1:2,]
colnames(gender_readmit_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

print(gender_readmit_table)

## CHI SQUARE GENDER FOR FULL TABLE


chisq.test(gender_readmit_table)

assocstats(gender_readmit_table)

colors <- c("red", "blue")
barplot(gender_readmit_table, main = "Readmissions by Gender", ylab = "Total", beside = TRUE, col = colors)
legend("topleft", c("female", "male"), fill = colors)
try1 <- data.table(gender_readmit_table)

p <- ggplot(try1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = gender, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Gender", subtitle = "From full data set")
p1 <- p + ylab("Number of patients") + xlab("Status")

p1

q <- ggplot(try1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
q <- q + labs(title = "Readmission status by Gender Percentage", subtitle = "From full data set")
q1 <- q + ylab("Percent by gender") + xlab("status")
q1

##ggarrange(p, q, ncol = 2, nrow = 1)

##ggarrange(p, q, ncol = 1, row = 2)

race_readmit <- diabetes_data[, c(3,50)]

race_readmit_table <- table(race_readmit)
race_readmit_table <- race_readmit_table[2:5,]
colnames(race_readmit_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")
rcolors <- c("red", "blue", "green", "yellow")

print(race_readmit_table)
##  CHI SQUARE FOR RACE FULL DATA

chisq.test(race_readmit_table)

assocstats(race_readmit_table)

barplot(race_readmit_table, main = "Readmission by Race", ylab = "Total", beside = TRUE, col = rcolors)
legend("topleft", legend = c("african/american", "Asian", "Caucasian", "Hispanic"), fill = rcolors)

race_readmit_table_1 <- data.table(race_readmit_table)

p <- ggplot(race_readmit_table_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = race, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Race", subtitle = "From full data set")
p2 <- p + ylab("Number of patients") + xlab("Status")
p2

q <- ggplot(race_readmit_table_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = race, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
q <- q + labs(title = "Readmission status by Race -  Percentage", subtitle = "From full data set")
q2 <- q + ylab("Percent by Race") + xlab("status")
q2

age_readmit <- diabetes_data[, c(5,50)]
age_readmit_table <- table(age_readmit)
colnames(age_readmit_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

print(age_readmit_table)


chisq.test(age_readmit_table)

assocstats(age_readmit_table)

barplot(age_readmit_table, main = "Readmission by Age", ylab="age", legend.text = TRUE, beside = TRUE, col = rainbow(3),args.legend = list(x = "topright", bty = "n", inset=c(-0.5, 0)))

age_readmit_table_1 <- data.table(age_readmit_table)
p <- ggplot(age_readmit_table_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = age, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Age", subtitle = "From full data set")
p3 <- p + ylab("Number of patients") + xlab("status")
p3

q <- ggplot(age_readmit_table_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = age, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5), check_overlap = TRUE)
q <- q + labs(title = "Readmission status by age Percentage", subtitle = "From full data set")
q3 <- q + ylab("Percent by age") + xlab("status")
q3

## ggarrange(p1, q1, p2, q2, p3, q3, heights = c(2,2,2,2,2,2), nrow = 3, ncol = 2)
```

Test Changes

```{r Changes, eval=TRUE, include = TRUE}
changes <- table(diabetes_data$change, diabetes_data$readmitted)
colnames(changes) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

chisq.test(changes)

assocstats(changes)


changes_1 <- data.table(changes)
colnames(changes_1) <- c("ChangedMeds", "readmitted", "N")
p <- ggplot(changes_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = ChangedMeds, cumulative = TRUE)) + geom_col()

p <- p + labs(title = "Readmission status by Change of Meds", subtitle  = "From full data set")
p <- p + ylab("Number of patients") + xlab("status")
p

q <- ggplot(changes_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = ChangedMeds, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5),,check_overlap = TRUE)
q <- q + labs(title = "Readmission status by Change of Meds Percentage", subtitle = "From full data set")
q <- q + ylab("Percentage") + xlab("status")
q

changy <- diabetes_data[diabetes_data$change == "Ch",]
table
```

## Or another way
## For all data, Chi-Square of readamission versus gender

```{r Alternative full set, eval =FALSE, include = FALSE}
gender_test <- table(diabetes_data$gender, diabetes_data$readmitted)

gender_test <- gender_test[1:2,]

chisq.test(gender_test)

assocstats(gender_test)


all_data_gender <- assocstats(gender_test)

print(all_data_gender)

changed_meds_test <- assocstats(changes)

print(changed_meds_test)

gender_changes <- table(diabetes_data$gender, diabetes_data$change)

print(changed_meds_test)

print(assocstats(gender_changes))
## now, summarize the data

weight_all = summary(diabetes_data$weight)
print(weight_all)


yup <- table(diabetes_data$patient_nbr)

print(quantile(yup))
## For all data, Chi-Square for  race versus admission data


race_test <- table(diabetes_data$race, diabetes_data$readmitted)

race_test <- race_test[1:5,]

all_data_race <- assocstats(race_test)

print(all_data_race)


## For all data, Chi-square for age versus readmission data


age_table <- table(diabetes_data$age, diabetes_data$readmitted)

print(age_table)


age_table <- age_table[2:10,]

chisq.test(age_table)


age_test <- assocstats(age_table)

print(age_test)


```
## Evaluate only patients with multiple encounter IDs

```{r Multiple, eval = TRUE}

Dupe_diabetes_data <- diabetes_data[diabetes_data$patient_nbr %in% names(which(table(diabetes_data$patient_nbr)>1)),]

## Duplicate patient ID, chi-square of  gender versus readmission


dupes_gender_table <- table(Dupe_diabetes_data$gender, Dupe_diabetes_data$readmitted)


dupes_gender_table <- dupes_gender_table[1:2,]
colnames(dupes_gender_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

print(dupes_gender_table)

dupes_gender_test <- assocstats(dupes_gender_table)

chisq.test(dupes_gender_table)

assocstats(dupes_gender_table)

print(dupes_gender_test)

dupes_gender_test_1 <- data.table(dupes_gender_table)

colnames(dupes_gender_test_1) <- c("gender", "readmitted", "N")
p <- ggplot(dupes_gender_test_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = gender, cumulative = TRUE)) + geom_col()

p <- p + labs(title = "Readmission status by Gender", subtitle =  "From multiple admisions data set")
p <- p + ylab("Number of patients") + xlab("Status")
p

p <- ggplot(dupes_gender_test_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))

p <- p + labs(title = "Readmission status by Gender Percentage",  subtitle =  "From multiple admisions data set")
p <- p + ylab("Percentage of patients") + xlab("Status")
p

## Duplicate patient ID, chi-square of race versus readmission

dupes_race_table <- table(Dupe_diabetes_data$race, Dupe_diabetes_data$readmitted)


## Remove the unknown races

dupes_race_table <- dupes_race_table[2:5,]
colnames(dupes_race_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

print(dupes_race_table)

dupes_race_test <- assocstats(dupes_race_table)

print(dupes_race_test)

dupes_race_test_1 <- data.table(dupes_race_table)

colnames(dupes_race_test_1) <- c("race", "readmitted", "N")

p <- ggplot(dupes_race_test_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = race, cumulative = TRUE)) + geom_col()

p <- p + labs(title = "Readmission status by Race",  subtitle =  "From multiple admisions data set")
p <- p + ylab("Number of patients") + xlab("Status")
p

p <- ggplot(dupes_race_test_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = race, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
p <- p + labs(title = "Readmission status by Race Percentage",  subtitle =  "From multiple admisions data set")
p <- p + ylab("Percentage of patients") + xlab("Status")
p

## Duplicate patient ID, chi-square of age versus readmission

dupe_age_table <- table(Dupe_diabetes_data$age, Dupe_diabetes_data$readmitted)


print(dupe_age_table)

dupe_age_table <- dupe_age_table[2:10,]

colnames(dupe_age_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")

dupe_age_test <- assocstats(dupe_age_table)

print(dupe_age_test)

dupe_age_test_1 <- data.table(dupe_age_table)
colnames(dupe_age_test_1) <- c("age", "readmitted", "N")
p <- ggplot(dupe_age_test_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = age, cumulative = TRUE)) + geom_col()

p <- p + labs(title = "Readmission status by Age", subtitle = "From multiple addmission data set")
p <- p + ylab("Number of patients") + xlab("Status")

p <- ggplot(dupe_age_test_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = age, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5),,check_overlap = TRUE)

p <- p + labs(title = "Readmission status by Race Percentage", subtitle = "From multiple addmission data set")
p <- p + ylab("Percentage of patients") + xlab("Status")

p
```
## Patients numbers only once (may have been readmitted)


```{r Single include, eval = TRUE}
No_duplicated_data <- diabetes_data[diabetes_data$patient_nbr %in% names(which(table(diabetes_data$patient_nbr)==1)),]

##print(head(No_duplicated_data))

gender_nodupes_table <- table(No_duplicated_data$gender, No_duplicated_data$readmitted)

colnames(gender_nodupes_table) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")


gender_nodupes_table <- gender_nodupes_table[1:2,]


print(gender_nodupes_table)

gender_nodupes_test <- assocstats(gender_nodupes_table)

print(gender_nodupes_test)

gender_nodupes_table_1 <- data.table(gender_nodupes_table)
colnames(gender_nodupes_table_1) <- c("gender", "readmitted", "N")
p <- ggplot(gender_nodupes_table_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = gender, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Gender", subtitle = "From single admission data set")
p <- p + ylab("Number of patients") + xlab("Status")
p

p  <- ggplot(gender_nodupes_table_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
p <- p + labs(title = "Readmission status by Gender Percentage", subtitle = "From single admission data set")
p <- p + ylab("Percentage of patients") + xlab("Status")

p

##  Now the race data

race_nodupes_table <- table(No_duplicated_data$race, No_duplicated_data$readmitted)

colnames(race_nodupes_table ) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")


race_nodupes_table <- race_nodupes_table[2:5,]

print(race_nodupes_table)

race_nodupes_test <- assocstats(race_nodupes_table)

print(race_nodupes_test)

race_nodupes_table_1 <- data.table(race_nodupes_table)
colnames(race_nodupes_table_1) <- c("race", "readmitted", "N")
p <- ggplot(race_nodupes_table_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = race, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Race", subtitle = "From single admission data set")
p <- p + ylab("Number of patients") + xlab("Status")
p

p <- ggplot(race_nodupes_table_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = race, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.5))
p <- p + labs(title = "Readmission status by Race Percentage", subtitle = "From single admission data set")
p <- p + ylab("Percentage of patients") + xlab("Status")

p

##  Now for the age data

age_nodupes_table <- table(No_duplicated_data$age, No_duplicated_data$readmitted)

colnames(age_nodupes_table ) <- c("re-ad < 30 days", "re-ad > 30 days", "no re-ad")



age_nodupes_table <- age_nodupes_table[2:10,]

print(age_nodupes_table)

age_nodupes_test <- assocstats(age_nodupes_table)

print(age_nodupes_test)

age_nodupes_table_1 <- data.table(age_nodupes_table)
colnames(age_nodupes_table_1) <- c("age", "readmitted", "N")
p <- ggplot(age_nodupes_table_1 %>% group_by(readmitted) , aes(x = readmitted, y = N, fill = age, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Readmission status by Age", subtitle = "From single admission data set")
p <- p + ylab("Number of patients") + xlab("Status")
p

p <- ggplot(age_nodupes_table_1 %>% group_by(readmitted) %>% mutate(perc = round(N/sum(N),2)), aes(x = readmitted, y = perc, fill = age, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.2), check_overlap = TRUE)
p <- p + labs(title = "Readmission status by Age Percentage", subtitle = "From single admission data set")
p <- p + ylab("Percentage of patients") + xlab("Status")

p
```
##  Other things to predict - number of procesdures

```{r Weird stuff, eval = TRUE, include = TRUE}

## remove ? for race

## For only with diabetes in diagnoses 1-3

dog <- diabetes_data
dog$diag_1 <- as.numeric(dog$diag_1)
dog$diag_2 <- as.numeric(dog$diag_2)
dog$diag_3 <- as.numeric(dog$diag_3)
diabetes_data$x <- dog$diag_1 >= 249 & dog$diag_1 < 251
diabetes_data$y <- dog$diag_2 >= 249 & dog$diag_2 < 251
diabetes_data$z <- dog$diag_3 >= 249 & dog$diag_3 < 251
diabetes_data$xyz <- diabetes_data$x == "TRUE" | diabetes_data$y == "TRUE" | diabetes_data$z == "TRUE"

coded <- diabetes_data[diabetes_data$xyz == "TRUE",]
dim(coded)
gender_code <- table(coded$gender, coded$readmitted)
gender_code <- gender_code[1:2,]
dim(gender_code)
print("The gender data is")
print(assocstats(gender_code))

age_code <- table(coded$age, coded$readmitted)
print("The age data is ")
print(assocstats(age_code))

race_code <- table(coded$race, coded$readmitted)
race_code <- race_code[2:5,]

print("The race data is ")
print(assocstats(race_code))

coded_first <- diabetes_data[diabetes_data$x == "TRUE",]
dim(coded_first)
race_code_first <- table(coded_first$race, coded_first$readmitted)
race_code_first <- race_code_first[2:5,]
print("The first diagnosis data is ")
print(assocstats(race_code_first))



```
## A t-test for the data - do males and females have the same mean lenght of stay in the hospital


```{r time in hospital , eval = TRUE}
male_stay <- diabetes_data[diabetes_data$gender =="Male",]
female_stay <- diabetes_data[diabetes_data$gender == "Female",]
t.test(male_stay$time_in_hospital, female_stay$time_in_hospital)

tablos <- table(diabetes_data$gender, diabetes_data$time_in_hospital)
tablos <- tablos[1:2,]
tablos_1 <- data.table(tablos)
colnames(tablos_1) <- c("gender", "length_of_stay", "total")
tablos_1$length_of_stay <- as.numeric(tablos_1$length_of_stay)
p <- ggplot(tablos_1 %>% group_by(length_of_stay) , aes(x = length_of_stay, y = total, fill = gender, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Length of Stay by Gender",  subtitle = "From full data set", caption = "From full data set")
p <- p + ylab("Number of patients") + xlab("Days")
p

q <- ggplot(tablos_1 %>% group_by(length_of_stay) %>% mutate(perc = round(total/sum(total),2)), aes(x = length_of_stay, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.2), check_overlap = TRUE)
q <- q + labs(title = "Length of Stay by Gender Percent",  subtitle = "From full data set", caption = "From full data set")
q <- q + ylab("Percentage") + xlab("Days")
q



male_nodupe_stay <- No_duplicated_data[No_duplicated_data$gender == "Male",]
female_nodupe_stay <- No_duplicated_data[No_duplicated_data$gender == "Female",]         
t.test(male_nodupe_stay$time_in_hospital, female_nodupe_stay$time_in_hospital)

tablos <- table(No_duplicated_data$gender, No_duplicated_data$time_in_hospital)
tablos <- tablos[1:2,]
tablos_1 <- data.table(tablos)
colnames(tablos_1) <- c("gender", "length_of_stay", "total")
tablos_1$length_of_stay <- as.numeric(tablos_1$length_of_stay)
p <- ggplot(tablos_1 %>% group_by(length_of_stay) , aes(x = length_of_stay, y = total, fill = gender, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Length of Stay by Gender",  subtitle = "Single Admission data subset")
p <- p + ylab("Number of patients") + xlab("Days")
p

q <- ggplot(tablos_1 %>% group_by(length_of_stay) %>% mutate(perc = round(total/sum(total),2)), aes(x = length_of_stay, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.2), check_overlap = TRUE)
q <- q + labs(title = "Length of Stay by Gender Percent",  subtitle = "From single admission data set", caption = "From single admission data set")
q <- q + ylab("Percentage") + xlab("Days")
q

male_dupe_stay <- Dupe_diabetes_data[Dupe_diabetes_data$gender == "Male",]
female_dupe_stay <-Dupe_diabetes_data[Dupe_diabetes_data$gender == "Female",]        
t.test(male_dupe_stay$time_in_hospital, female_dupe_stay$time_in_hospital)

tablos <- table(Dupe_diabetes_data$gender, Dupe_diabetes_data$time_in_hospital)
tablos <- tablos[1:2,]
tablos_1 <- data.table(tablos)
colnames(tablos_1) <- c("gender", "length_of_stay", "total")
tablos_1$length_of_stay <- as.numeric(tablos_1$length_of_stay)
p <- ggplot(tablos_1 %>% group_by(length_of_stay) , aes(x = length_of_stay, y = total, fill = gender, cumulative = TRUE)) + geom_col()
p <- p + labs(title = "Length of Stay by Gender", subtitle  = "Multiple admissions data set", caption = "Multiple admissions data set")
p <- p + ylab("Number of patients") + xlab("Days")
p

q <- ggplot(tablos_1 %>% group_by(length_of_stay) %>% mutate(perc = round(total/sum(total),2)), aes(x = length_of_stay, y = perc, fill = gender, cumulative = TRUE)) + geom_col() +
 geom_text(aes(label = paste0(perc*100,"%")), 
              position = position_stack(vjust = 0.2), check_overlap = TRUE)
q <- q + labs(title = "Length of Stay by Gender Percent",  subtitle = "From multiple admission data set", caption = "From multiple admission data set")
q <- q + ylab("Percentage") + xlab("Days")
q

```

## Now to test to see if Medicare patients have differing results

``` {r medicare, eval = TRUE, include = TRUE}

medi <- diabetes_data[diabetes_data$payer_code == "MC",]
no_medi <- diabetes_data[diabetes_data$payer_code != "MC",]
total_no_perc <- sum(diabetes_data$readmitted == "NO")/dim(diabetes_data)[1]
total_lt_30 <- sum(diabetes_data$readmitted == "<30")/dim(diabetes_data)[1]
total_mt_30 <- sum(diabetes_data$readmitted == ">30")/dim(diabetes_data)[1]
total_no_medi <- sum(medi$readmitted == "NO")/dim(medi)[1]
total_lt30_medi <- sum(medi$readmitted == "<30")/dim(medi)[1]
total_mt30_medi <- sum(medi$readmitted == ">30")/dim(medi)[1]
total_no_medi_no <- sum(no_medi$readmitted == "NO")/dim(no_medi)[1]
total_no_medi_lt30 <- sum(no_medi$readmitted == "<30")/dim(no_medi)[1]
total_no_medi_mt30 <- sum(no_medi$readmitted == ">30")/dim(no_medi)[1]
frame_it <- data.frame(total_no_perc, total_lt_30, total_mt_30)
frame_jt <- data.frame(total_no_medi, total_lt30_medi, total_mt30_medi)
frame_kt <- data.frame(total_no_medi_no, total_no_medi_lt30, total_no_medi_mt30)
colnames(frame_it) <- c("no_re-ad", "re-ad_lt_30", "re-ad_mt_30")
colnames(frame_jt) <- c("no_re-ad", "re-ad_lt_30", "re-ad_mt_30")
colnames(frame_kt) <- c("no_re-ad", "re-ad_lt_30", "re-ad_mt_30")
framez <- rbind(frame_it, frame_jt, frame_kt)
framez <- 1000* framez
chisq.test(framez)

```